---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# openmarawi: An Interface to the Open Marawi Database

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The citizens of Marawi have a right to the data and maps about their home city. When problems are complex, helping people find useful maps (access) can aid them both in finding themselves in the map (understanding) and making the map by themselves (ownership).
 
Open data and useful maps can help empower citizens in mapmaking, placemaking, and decision-making because it can help citizens and interested parties in understanding the issues spatially. It is practical in deliberating, deciding, and delivering the rehabilitation of Marawi City.

## Installation

<!---
You can install the released version of openmarawi from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("openmarawi")
```
--->

`openmarawi` packages is not yet available on CRAN.

The development version of the `openmarawi` package can be installed from GitHub with:

```{r install, eval = FALSE}
if (!require(remotes)) install.packages("remotes")
remotes::install_github("panukatan/openmarawi")
```

## Usage
